Title

### 2013-01-25 inc/gun/gun_design.tex
comment on alignment

>>>>

Re-alignment of cathode and anode is sometimes necessary to direct the emitted beam down the center axis of the column.
To facilitate this, the prototype column has the photocathode and Wehnelt mounted on the end of the high voltage feedthrough, which is in turn mounted on a two axis alignment mechanism.
Although this mechanism, called a ``port aligner,'' is typically used to couple two non-colinear vacuum ports, for use in this instrument it has been modified to be able to manually adjust the aligner during use.
In contrast to this flexibility, the anode is mounted to column using Kimball Physics's ``eV Parts'' mounting systems.
These strictly manufactured mounting hardwares ensure that the anode is properly aligned with the remainder of the microscope column.
Thus, by iteratively repositioning the input laser and then the gun alignment, the beam may be walked to pass as near as possible down the axis of the column.
